\racets: Policy{-}Agnostic Programming in Racket

### 2018-07-24 paper/paper.tex
merging

Because the applied function can be stateful, faceted execution also
maintains the current privilege level in a \emph{program counter} (PC). The
program counter is a property of the current evaluation context and is used
to build facets when writes are made to the store in a privileged context.
For example, if a stateful function ``splits'' when applied on both the positive and negative
facets of a value faceted by a label $\blue{\ell}$, and on the positive branch
the function uses $\texttt{set!}$ to mutate a variable $x$ from $2$ to $3$,
FE semantics will set $x$ to $\facet{\ell}{3}{2}$ so that the value $3$
cannot be leaked from the secure context (speculative execution under the
$\blue{+\ell}$ facet). This is because, for the duration of the the app ``split'',
the evaluation context records that all values are implicitly guarded by $\blue{+\ell}$
and then $\blue{-\ell}$, respectively. If the semantics for $\texttt{set!}$ does
not make this faceting explicit, a senstive value could leak from one PC to another.
We expand upon these subtleties in Section~\ref{sec:semantics},
where we present a complete semantics for faceted execution.

@@

\begin{figure}
\begin{displaymath}
  \begin{array}{lcrcl}
    \blue{c} & \blue{\in} & \blue{const} & \blue{::=} & \blue{'() \mid \code{true} \mid \code{false} \mid \ldots} \\
    \blue{x} & \blue{\in} & \blue{var} & \blue{::=} & \langle\textit{program variables}\rangle  \\
    \blue{e} & \blue{\in} & \blue{exp} & \blue{::=} & \blue{c} \mid \blue{x} \\
    & & & \blue{\mid} & \blue{(\lambda ~ (x) ~ e) \mid (e ~ e)} \\
    & & & \blue{\mid} & \blue{(\code{box} ~ e) \mid (\code{unbox} ~ e) \mid (\code{set!} ~ e ~ e)} \\
    & & & \blue{\mid} & \blue{(\code{let-label} ~ x ~ e ~ e)} \\
    & & & \blue{\mid} & \blue{(\code{facet} ~ e ~ e ~ e)} \\
    & & & \blue{\mid} & \blue{(\code{obs} ~ e ~ e ~ e)} \\
  \end{array}
\end{displaymath}
\label{fig:syntax}
\caption{Syntax of \lang. Forms unique to facets are shown in \fcol{red}.}
\end{figure}

>>>>

Because the applied function can be stateful, faceted execution also
vmaintains the current privilege level in a \emph{program counter} (PC). The
program counter is a property of the current evaluation context and is used
to build facets when writes are made to the store in a privileged context.
For example, if a stateful function ``splits'' when applied on both the positive and negative
facets of a value faceted by a label $\blue{\ell}$, and on the positive branch
the function uses $\texttt{set!}$ to mutate a variable $x$ from $2$ to $3$,
FE semantics will set $x$ to $\facet{\ell}{3}{2}$ so that the value $3$
cannot be leaked from the secure context (speculative execution under the
$\blue{+\ell}$ facet). This is because, for the duration of the the app ``split'',
the evaluation context records that all values are implicitly guarded by $\blue{+\ell}$
and then $\blue{-\ell}$, respectively. If the semantics for $\texttt{set!}$ does
not make this faceting explicit, a senstive value could leak from one PC to another.
We expand upon these subtleties in Section~\ref{sec:semantics},
where we present a complete semantics for faceted execution.

After making various moves, we eventually want to reveal the game
boards, pulling the positive view out of \code{alice-board} to display
Alice's board. To do this, we must \emph{observe} the facet with an
\code{obs} form. Because Alice's board is faceted with
\code{alice-label}, we specify that we want to observe
\code{alice-label} and pass in an argument to that label showing that
Alice is indeed the person observing the facet:

\begin{lstlisting}[language=Racket,escapechar=|,name=example]
(obs alice-label 1 alice-board) ; Returns Alice's board
\end{lstlisting}

If we had passed any value other than $1$ into the \code{obs} form,
Alice's policy would return \code{false}. In this case, the \code{obs}
form would reduce to $\blue{\star}$, and the program would fail
(indicating that someone other than Alice attempted to view her
board).

@@

\begin{figure*}
\begin{displaymath}
  \begin{array}{lcrcl}
    \blue{c} & \blue{\in} & \blue{const} & \blue{::=} & \blue{'() \mid \code{true} \mid \code{false} \mid \ldots} \\
    \blue{x} & \blue{\in} & \blue{var} & \blue{::=} & \langle\textit{program variables}\rangle  \\
    \blue{e} & \blue{\in} & \blue{exp} & \blue{::=} & \blue{c} \mid \blue{x} \\
    & & & \blue{\mid} & \blue{(\lambda ~ (x) ~ e) \mid (e ~ e)} \\
    & & & \blue{\mid} & \blue{(\code{box} ~ e) \mid (\code{unbox} ~ e) \mid (\code{set!} ~ e ~ e)} \\
    & & & \blue{\mid} & \blue{(\code{let-label} ~ x ~ e ~ e)} \\
    & & & \blue{\mid} & \blue{(\code{facet} ~ e ~ e ~ e)} \\
    & & & \blue{\mid} & \blue{(\code{obs} ~ e ~ e ~ e)} \\
  \end{array}
\end{displaymath}
\caption{Syntax of \lang.}
\label{fig:syntax}
\end{figure*}
